Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-03 paper/paper.tex
Noam's comments

\begin{compactdesc}
\item[Character $n$-grams] The number of character 1-, 2-, and
  3-grams. 69.94\%.
\item[Frequent character $n$-grams] Only those character $n$-grams
  that are observed more than $m$ times in the corpus are
  considered. ???
\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
\item[Document length] The number of tokens in the text. 11.81\%.
\item[Pronouns] The number of each pronoun. 22.81\%.
\item[Punctuation] The number of each punctuation mark. 27.41\%.
\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the authors L1. We use the counts (???) of the first
  and last three words in each sentence as features. 53.03\%.
\item[Cohesive markers] These are function words (and short phrases)
  that have a strong discourse function in texts, contributing to its
  cohesiveness. 25.71\%.
\item[Cohesive verbs] ???. 22.85\%.
\item[Function words] The number of occurrences of each word from a
  pre-defined list of 100 most frequent words in English (excluding
  punctuation). 42.47\%.
\item[Contextual function words, bigrams] Pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. 62.79\%
\item[Contextual function words, trigrams] Same as above, but counting
  3-grams consisting of two function words and the POS tag of the
  third word in the 3-gram. 62.32\%.
\item[Lemmas] The number of each of the most frequent lemmas in the
  text. ???. 58.95\%.
\item[Prompt] Conjunction of the character $n$-gram features defined
  above with the prompt; since the prompt contributes information on
  the domain, it is likely that some words (and, hence, character
  sequences) will occur more frequently with some prompts than with
  others. 65.09\%.
\item[Misspelling features] ???. 37.29\%.
\item[Brown] ???
\item[Restored] ???
\end{compactdesc}

@@

\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}}

@@

\subsection{\feat{Pron}: pronouns\nss{?}}

>>>>

\begin{compactdesc}
\item[Character $n$-grams] The number of character 1-, 2-, and
  3-grams. 69.94\%.
\item[Frequent character $n$-grams] Only those character $n$-grams
  that are observed more than $m$ times in the corpus are
  considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
\item[Document length] The number of tokens in the text. 11.81\%.
\item[Pronouns] The number of each pronoun. 22.81\%.
\item[Punctuation] The number of each punctuation mark. 27.41\%.
\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the authors L1. We use the counts (???) of the first
  and last three words in each sentence as features. 53.03\%.
\item[Cohesive markers] These are 40 function words (and short phrases)
  that have a strong discourse function in texts \nt{such as 'however', 'becuase', 'in fact' etc}, contributing to its
  cohesiveness. 25.71\%. \nt{Translators tend to spell out implicit utterances and render them explicitly in the target text (REFERENCE TO BLUM-KULKA); MAYBE APPEND THE LIST IN THE END?} 
\item[Cohesive verbs] \nt{This is a list of manually compiled verbs that serve, like `cohesive markers' to spell out implicit utterances; they include, among others, `indicating', `implying' and `containing'. Same, consider appending the list}. 22.85\%.
\item[Function words] The number of occurrences of each word from a
  pre-defined list of 100 \nt{did you use only 100? it should be 400 and the reference should be to Koppel and Ordan} most frequent words in English (excluding
  punctuation). 42.47\%.
\item[Contextual function words, bigrams] Pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. 62.79\%
\item[Contextual function words, trigrams] Same as above, but counting
  \nt{2- or} 3-grams consisting of one or two function words (respectively) and the POS tag of the third word \nt{character?} in the \nt{2- or} 3-gram. 62.32\%.
\item[Lemmas] \nt{these should be actually `stems' as produced by the Stanford tagger} The number of each of the most frequent lemmas in the
  text. ???. 58.95\%.
\item[Prompt] Conjunction of the character $n$-gram features defined
  above with the prompt; since the prompt contributes information on
  the domain, it is likely that some words (and, hence, character
  sequences) will occur more frequently with some prompts than with
  others. 65.09\%.
\item[Misspelling features] ???. 37.29\%.
\item[Brown] ???
\item[Restored] ???
\end{compactdesc}

@@

\subsection{\feat{CxtFxn}: Contextual function words\nss{does this subsume pronouns?}} \nt{yes}

@@

\subsection{\feat{Pron}: pronouns\nss{?}} \nt{A list of 25 pronouns in English, again, append list}
